---
title: 'Simulations of Estimating Long-term Average Exposures in Cookstove Studies'
author: ""
date: '`r format(Sys.time(), "%d %B %Y")`'
output:
  bookdown::html_document2:
    self_contained: true
    split_by: none
    output_dir: '../' 
    toc: yes
    toc_float: yes
fontsize: 10pt
---
    
<!-- # includes: -->
<!-- # in_header: preamble-mathjax.tex -->
<!-- bibliography: PrincipalStratBib.bib -->


```{r setup, include=FALSE}
library(knitr)

knitr::opts_chunk$set(error=TRUE, echo=FALSE)
knitr::knit_hooks$set(inline = function(x) { if(!is.numeric(x)){ x }else{ prettyNum(x, big.mark=",") } })
knitr::opts_chunk$set(fig.path = "fig/")
knitr::opts_chunk$set(fig.align='center') 
knitr::opts_chunk$set(tab.align='center')

code_dir <- ""
results_dir <- "results/"

library(tidyverse)
library(here)

library(bercs)

library(lme4)
library(performance)
library(splines)
library(parallel)

q25 <- function(w, ...) quantile(w, probs=0.25, ...)
q75 <- function(w, ...) quantile(w, probs=0.75, ...)
```

```{r setup_stan, echo=FALSE, include=FALSE}
# library(rstan)
# rstan_options(auto_write = TRUE)
# options(mc.cores = max(1, parallel::detectCores()-2))
```
# Setup

## Temporal trends

```{r trend_funs}
fA <- function(w) 0*w
fB <- function(w) 0.5*sinpi(2*w)  
fC <- function(w, start_interval_length=0, interval_gap,interval_length, J)  -0.1*(w - (start_interval_length + ifelse(length(interval_gap)>1, interval_length + max(interval_gap), J*(interval_length + interval_gap)))/2)
fD <- function(w, start_interval_length=0, interval_gap,interval_length, J) 0.5*sinpi(2*w)  +  -0.5*(w - (start_interval_length + ifelse(length(interval_gap)>1, interval_length + max(interval_gap), J*(interval_length + interval_gap)))/2)
fE <- function(w)  -0.5*sinpi(2*w) + -0.1*sinpi(12*w) - 0.2*sinpi(4*(w-0.2))
fF <- function(w)  0.2279585- 0.1* exp(-2*sinpi(2*w)) + 0.05*sinpi(12*w)
```


```{r trends_plot, cache=TRUE, fig.height=4, fig.width=4.5}
x <- seq(0, 2, length=501)[-501]
fdemo <- data.frame(x=x) %>%
  mutate(A=fA(x),
         B=fB(x),
         C=fC(x, J=8, interval_gap=0, interval_length=0.25),
         D=fD(x, J=8, interval_gap=0, interval_length=0.25),
         E=fE(x),
         F=fF(x)) %>%
  pivot_longer(-x, names_to="Trend") %>%
  mutate(date=lubridate::date_decimal(x)) %>%
  mutate(date=lubridate::date(date))
ggplot(fdemo) + theme_bw() + 
  geom_path(aes(x=date, y=value, col=Trend, lty=Trend)) +
  scale_x_date(date_labels = "%b") +
  xlab("Date") +
  ylab("Trend Value")
```

## Simulation Functions

```{r}
source("simulation_functions.R")
```

```{r}
run_many_wrapper <- function(design,
                             setting,
                             J,
                             J1=J,
                             J2=J,
                             firstgroup=1,
                             B=10,
                             n=200,
                             cores=1,
                             time_spline_df=6,
                             time_spline_df2=4) {
  
  
  if (design==0 ){
    times= rep(1:J, times=c(n*2))
       study_type="parallel"
 interval_length=0
    interval_gap=0
    random_initial_only=FALSE
    start_interval_length=0
    truth_timerange_min=0
    truth_timerange_max=0
  } else if (design==1) {
    times= "sample"
        study_type="parallel"
interval_length=0.0833
    interval_gap=0.1666
    random_initial_only=FALSE
    start_interval_length=0
  } else if (design==2) {
    times= "sample"
       study_type="parallel"
 interval_length=0.0833
    interval_gap=0.1666
    random_initial_only=FALSE
    start_interval_length=0.2
  }  else if (design==3) {
    times= "sample"
        study_type="parallel"
interval_length=0.1
    interval_gap=c(0, 0.2, 0.45, 0.95)
    random_initial_only=FALSE
    start_interval_length=0
  }   else if (design==4) {
    times= "sample"
        study_type="parallel"
interval_length=0.1
    interval_gap=c(0, 0.2, 0.45, 0.95)
    random_initial_only=FALSE
    start_interval_length=1.5
  }   else if (design==5) {
    times= "sample"
        study_type="parallel"
    interval_length=0.1
    interval_gap=c(0, 0.2, 0.45, 0.7, 0.95, 1.45)
    random_initial_only=FALSE
    start_interval_length=1.5
  }  else if (design==6) {
    times= "sample"
    study_type="crossover"
   interval_length=0.0833
    interval_gap=0.1666
    random_initial_only=FALSE
    start_interval_length=0
  } else if (design==7) {
    times= "sample"
    study_type="crossover"
   interval_length=0.0833
    interval_gap=0.1666
    random_initial_only=FALSE
    start_interval_length=1
  }
  
  
  if (setting=="A"){
    sigA2 <-  0.5
    sigE2 <-  1
    groupmeans <- c(4, 5)
    timefn <- fA
  } else if (setting=="B"){
    sigA2 <-  0.5
    sigE2 <-  1
    groupmeans <- c(4, 5)
    timefn <- fB
  } else if (setting=="C"){
    sigA2 <-  0.5
    sigE2 <-  1
    groupmeans <- c(4, 5)
    timefn <- function(w) fC(w, 
                             start_interval_length=start_interval_length,
                             interval_gap=interval_gap,
                             interval_length=interval_length,
                             J=J)
  } else if (setting=="D"){
    sigA2 <-  0.5
    sigE2 <-  1
    groupmeans <- c(4, 5)
    timefn <- function(w) fD(w, 
                             start_interval_length=start_interval_length,
                             interval_gap=interval_gap,
                             interval_length=interval_length,
                             J=J)
    } else if (setting=="E"){
    sigA2 <-  0.5
    sigE2 <-  1
    groupmeans <- c(4, 5)
    timefn <- fE
  } else if (setting=="F"){
    sigA2 <-  0.5
    sigE2 <-  1
    groupmeans <- c(4, 5)
    timefn <- fF
  }
  
  res <- run_many(B=B,
                  study_type=study_type,
          ngroups=2,
          n=n, # per group
          J=J,
          J1=J1,
          J2=J2,
          firstgroup=firstgroup,
          groupmeans=groupmeans,
          sigE=sqrt(sigE2),
          sigA=sqrt(sigA2),
          verbose=FALSE,
          timefn=timefn, ## **ASSUMED TO HAVE MEAN ZERO**
          times=times,
          time_spline_df=time_spline_df,
          time_spline_df2=time_spline_df2,
          truth_timerange_min=0,
          truth_timerange_max=start_interval_length + (J-1)*interval_gap + J*interval_length,
          cores=cores,
          interval_length=interval_length,
          interval_gap=interval_gap,
          random_initial_only=random_initial_only,
          start_interval_length=start_interval_length)
  res$setting <- setting
  res$design <- design
  res$B <- B
  res$J <- J
  res$J1 <- J1
  res$J2 <- J2
  res
}
```


Design description:


|Design	| Study Type	| Study Duration (months) |	J	| Description |
|:--:|:----|:--:|:-:|:----------------------|
| Design 1	| Parallel	| 4-16 months	| 2-6	| Measurements spaced three months apart (i.e., all participants with a visit in each of months 1, 4, 7, etc.). The time for each visit is randomly selected within a one-month window. |
| Design 2	| Parallel	| 16-28 months	| 2-6	| Measurements spaced three months apart, but initial visit is randomly chosen within first year (therefore, all months during the year contain visits). The time for each visit is randomly selected within a one-month window.
| Design 3 |	Parallel	| 12 months	| 4	| Measurements made in months 1, 3, 6, and 12. The time for each visit is randomly selected within a five-week window.
| Design 4 | 	Parallel	| 30 months	| 4	| Measurements made in months 1, 3, 6, and 12, except initial visit for each household is randomly chosen within first 18 months. The time for each visit is randomly selected within a five-week window.
| Design 5 | Parallel	| 36 months	| 6	| Measurements made in months 1, 3, 6, 9, 12, and 18, except initial visit for each household is randomly chosen within first 18 months. The time for each visit is randomly selected within a five-week window.
| Design 6 |	Stepped-wedge	| 16 months	| 6	|Either 2 or 4 measurements in each stove group. Measurements made every three months (i.e., months 1, 4, 7, 10, 13, 16). The time for each visit is randomly selected within a one-month window.
| Design 7 |	Stepped-wedge	| 28 months	| 6 |	Either 2 or 4 measurements in each stove group. Measurements made every three months (i.e., months 1, 4, 7, 10, 13, 16), except initial visit is randomly chosen within first year. The time for each visit is randomly selected within a one-month window.

# Run Simulations

```{r flag_design_changes, cache=TRUE}
 
```

## Design 1
```{r des1, echo=FALSE, cache=TRUE, dependson="flag_design_changes"}
# Design 1
sim_design1 <- data.frame()
for (setting in c("A", "B", "C", "D", "E", "F")){
  for (J  in 2:6){
res <- run_many_wrapper(setting=setting,
                        design=1,
                        J=J,
                        B=6, # Set to 100
                        cores=6,
                        time_spline_df2=J)
sim_design1 <- bind_rows(sim_design1, res)
}
}
save(sim_design1, file=paste0(results_dir, "Sim_design1.RData"))
rm(sim_design1)
```


## Design 2
```{r des2, echo=FALSE, cache=TRUE, dependson="flag_design_changes"}
# Design 2
sim_design2 <- data.frame()
for (setting in c("A", "B", "C", "D", "E", "F")){
  for (J  in 2:6){
res <- run_many_wrapper(setting=setting,
                        design=2,
                        J=J,
                        B=6,
                       cores=6,
                        time_spline_df2=J)
sim_design2 <- bind_rows(sim_design2, res)
}
}
save(sim_design2, file=paste0(results_dir, "Sim_design2.RData"))
rm(sim_design2)
```

## Design 3
```{r des3, echo=FALSE, cache=TRUE, dependson="flag_design_changes"}
# Design 3
sim_design3 <- data.frame()
for (setting in c("A", "B", "C", "D", "E", "F")){
  for (J  in 4){
    res <- run_many_wrapper(setting=setting,
                            design=3,
                            J=J,
                        B=6,
                       cores=6,
                        time_spline_df2=4)
    sim_design3 <- bind_rows(sim_design3, res)
  }
}
save(sim_design3, file=paste0(results_dir, "Sim_design3.RData"))
rm(sim_design3)
```

## Design 4
```{r des4, echo=FALSE, cache=TRUE, dependson="flag_design_changes"}
sim_design4 <- data.frame()
for (setting in c("A", "B", "C", "D", "E", "F")){
  for (J  in 4){
    res <- run_many_wrapper(setting=setting,
                            design=4,
                            J=J,
                        B=6, 
                        cores=6,
                        time_spline_df2=10)
    sim_design4 <- bind_rows(sim_design4, res)
  }
}
save(sim_design4, file=paste0(results_dir, "Sim_design4.RData"))
rm(sim_design4)
```

## Design 5
```{r des5, echo=FALSE, cache=TRUE, dependson="flag_design_changes"}
sim_design5 <- data.frame()
for (setting in c("A", "B", "C", "D", "E", "F")){
  for (J  in 6){
    res <- run_many_wrapper(setting=setting,
                            design=5,
                            J=J,
                        B=6,
                       cores=6,
                        time_spline_df2=12)
    sim_design5 <- bind_rows(sim_design5, res)
  } 
}
save(sim_design5, file=paste0(results_dir, "Sim_design5.RData"))
rm(sim_design5)
```


## Design 6
```{r des6, echo=FALSE, cache=TRUE, dependson="flag_design_changes"}
sim_design6 <- data.frame()
for (setting in c("A", "B", "C", "D", "E", "F")){
  for (J  in 6){
    res <- run_many_wrapper(setting=setting,
                            design=6,
                            J=6,
                            J1=2,
                            J2=4,
                            firstgroup=1,
                        B=6,
                       cores=6,
                        time_spline_df2=5) 
    sim_design6 <- bind_rows(sim_design6, res)
  }
}
save(sim_design6, file=paste0(results_dir, "Sim_design6.RData"))
rm(sim_design6)
```


## Design 7
```{r des7, echo=FALSE, cache=TRUE, dependson="flag_design_changes"}
sim_design7 <- data.frame()
for (setting in c("A", "B", "C", "D", "E", "F")){
  for (J  in 6){
    res <- run_many_wrapper(setting=setting,
                            design=7,
                            J=6,
                            J1=2,
                            J2=4,
                            firstgroup=1,
                        B=6,
                       cores=6,
                        time_spline_df2=9)
    sim_design7 <- bind_rows(sim_design7, res)
  } 
}
save(sim_design7, file=paste0(results_dir, "Sim_design7.RData"))
rm(sim_design7)
```

