---
title: "Simulation Results"
author: ""
date: '`r format(Sys.time(), "%d %B %Y")`'
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
library(tidyverse)

knitr::opts_chunk$set(error=TRUE, echo=FALSE)
knitr::knit_hooks$set(inline = function(x) { if(!is.numeric(x)){ x }else{ prettyNum(x, big.mark=",") } })
knitr::opts_chunk$set(fig.path = "../Figures/Exposure_Simulations_v2/Separate_set/")
knitr::opts_chunk$set(fig.align='center') 
knitr::opts_chunk$set(tab.align='center')

results_dir <- "results/"

```


# Load Results 

```{r}
load(paste0(results_dir, "Sim_design1.RData"))
load(paste0(results_dir, "Sim_design1A23.RData"))
load(paste0(results_dir, "Sim_design2.RData"))
load(paste0(results_dir, "Sim_design3.RData"))
load(paste0(results_dir, "Sim_design4.RData"))
load(paste0(results_dir, "Sim_design5.RData"))
load(paste0(results_dir, "Sim_design6.RData"))
load(paste0(results_dir, "Sim_design7.RData"))

sim_results <- bind_rows(sim_design1,
                         sim_design1A23,
                         sim_design2,
                         sim_design3,
                         sim_design4,
                         sim_design5,
                         sim_design6)

```


```{r cacl-relative-MSE}
sim_results <- sim_results %>%
  mutate(MSE_ratio_hh=MSE.hh_avg.TobsPobs/MSE.splinetime.TobsPobs,
       MSE_ratio_notime=MSE.wgroup.TobsPobs/MSE.splinetime.TobsPobs,
       MSE_ratio_factime=MSE.factime.TobsPobs/MSE.splinetime.TobsPobs,
       MSE_ratio_splinetime2=MSE.splinetime2.TobsPobs/MSE.splinetime.TobsPobs) %>%
  mutate(MSE_ratio2_hh=MSE.hh_avg.TobsPobs/MSE.splinetime2.TobsPobs,
       MSE_ratio2_notime=MSE.wgroup.TobsPobs/MSE.splinetime2.TobsPobs,
       MSE_ratio2_factime=MSE.factime.TobsPobs/MSE.splinetime2.TobsPobs,
       MSE_ratio2_splinetime=MSE.splinetime.TobsPobs/MSE.splinetime2.TobsPobs)
```



```{r cacl-relative-RMSE}
sim_results <- sim_results %>%
  mutate(RMSE_ratio_hh=sqrt(MSE_ratio_hh),
       RMSE_ratio_notime=sqrt(MSE_ratio_notime),
       RMSE_ratio_factime=sqrt(MSE_ratio_factime),
       RMSE_ratio_splinetime2=sqrt(MSE_ratio_splinetime2))  %>%
   mutate(RMSE_ratio2_hh=sqrt(MSE_ratio2_hh),
       RMSE_ratio2_notime=sqrt(MSE_ratio2_notime),
       RMSE_ratio2_factime=sqrt(MSE_ratio2_factime),
       RMSE_ratio2_splinetime=sqrt(MSE_ratio2_splinetime)) 
```



```{r create-results-subsets}
MSE_results <- sim_results %>%
    select(-contains("sigA")) %>%
  select(-contains("sigE")) %>%
    select(-contains("ratio")) %>%
  pivot_longer(cols=contains(".")) %>%
  separate(name,
           into=c("metric", "model", "comparison"),
           sep="\\.") %>%
  filter(metric=="MSE")  %>%
  filter(comparison=="TobsPobs")  %>%
  mutate(Model=case_when(model=="factime"~"MM: Time as Factor",
                       model=="hh_avg"~"HH Avg.",
                       model=="lintime"~"MM: Linear Time",
                       model=="nogroup"~"MM: No Time, No Group Effect",
                       model=="wgroup"~"MM: No Time",
                       model=="splinetime"~"MM: Time Spline",
                       model=="splinetime2"~"MM: Time Spline",
                       TRUE~model))
```

# Design 1

## Setting A

### Absolute MSE
#### All models
```{r mse-design1-settingA-allModels,  fig.height=4.5, fig.width=4.5}
g_ratio <- MSE_results %>%
  filter(design %in% c(1)) %>%
  filter(setting %in% c("A")) %>%
  ggplot() +
  theme_bw() +
   geom_path(aes(x=J,
                 y=value,
                 col=Model)) +
  geom_point(aes(x=J,
                 y=value,
                 col=Model,
                 shape=Model)) +
  ylab("MSE") + 
  guides(color=guide_legend(nrow=3)) + 
  theme(legend.position="bottom")
g_ratio
```

#### Subset of Models
```{r mse-design1-settingA, fig.height=4.5, fig.width=4.5}
# Plot MSE for Design 1, Setting A
g_mse <- MSE_results %>%
  filter(design %in% c(1),
         setting %in% c("A")) %>%
    filter(model %in% c("hh_avg", "nogroup", "wgroup")) %>%

  ggplot() +
  theme_bw() +
    geom_path(aes(x=J,
                 y=value,
                 col=Model)) +
  geom_point(aes(x=J,
                 y=value,
                 col=Model,
                 shape=Model), size=2) +
  ylab("MSE") +
  xlab("Number of Measurements per Household (J)")+ 
  guides(color=guide_legend(nrow=2)) + 
  theme(legend.position="bottom") +
  ylim(c(0, 0.5))
g_mse
```

### Absolute RMSE

Designed to compare effect of ignoring stove in the model, as well as the role of additional measurements.

```{r rmse-design1-settingA, fig.height=4.5, fig.width=4.5}
# Plot RMSE for Design 1, Setting A
g_rmse <- MSE_results %>%
  filter(design %in% c(1),
         setting %in% c("A")) %>%
    filter(model %in% c("hh_avg", "nogroup", "wgroup")) %>%

  ggplot() +
  theme_bw() +
    geom_path(aes(x=J,
                 y=sqrt(value),
                 col=Model)) +
  geom_point(aes(x=J,
                 y=sqrt(value),
                 col=Model,
                 shape=Model), size=2) +
  ylab(expression("RMSE (Log "~mu~"g/m"^3~")")) +
  xlab("Number of Measurements per Household (J)")+ 
  guides(color=guide_legend(nrow=2)) + 
  theme(legend.position="bottom") +
  ylim(c(0, 1))
g_rmse
```

## All Settings

### Absolute MSE


```{r mse-design1-dfJ, fig.height=4.5, fig.width=4.5}
g_ratio <- MSE_results %>%
  filter(design %in% c(1)) %>%
  filter(!setting %in% c("B2")) %>%
  rename(Trend=setting) %>%
  mutate(Design=case_when(design==1~"1 -- Parallel",
                          design==2~"2 -- Parallel, Staggered Baseline")) %>%
  filter(model %in% c("splinetime2", "wgroup", "hh_avg")) %>%
  ggplot() +
  theme_bw() +
  geom_path(aes(x=J,
                 y=value,
                 col=as.factor(Model))) +
  geom_point(aes(x=J,
                 y=value,
                 col=as.factor(Model),
                 shape=as.factor(Model))) +
  ylab("MSE") + 
  xlab("Number of Measurements per Household (J)")+ 
  facet_wrap(~Trend,
             scales="free_x",
             labeller=labeller(Trend = label_both,
                               design= label_both)) +
  guides(color=guide_legend(nrow=1)) + 
  theme(legend.position="bottom") +
  scale_color_discrete(name="Design:")  +
  scale_shape_discrete(name="Design:")  +
    scale_y_continuous(breaks=c(0, 0.1, 0.2, 0.3, 0.4, 0.5), limits=c(0, 0.55))
g_ratio
```


### Absolute RMSE

```{r rmse-design1-dfJ, fig.height=4.5, fig.width=4.5}
g_ratio <- MSE_results %>%
  filter(design %in% c(1)) %>%
  filter(!setting %in% c("B2")) %>%
  rename(Trend=setting) %>%
  mutate(Design=case_when(design==1~"1 -- Parallel",
                          design==2~"2 -- Parallel, Staggered Baseline")) %>%
  filter(model %in% c("splinetime2", "wgroup", "hh_avg")) %>%
  ggplot() +
  theme_bw() +
  geom_path(aes(x=J,
                 y=sqrt(value),
                 col=as.factor(Model))) +
  geom_point(aes(x=J,
                 y=sqrt(value),
                 col=as.factor(Model),
                 shape=as.factor(Model))) +
  ylab(expression("RMSE (Log "~mu~"g/m"^3~")")) +
  xlab("Number of Measurements per Household (J)")+ 
  facet_wrap(~Trend,
             scales="free_x",
             labeller=labeller(Trend = label_both,
                               design= label_both)) +
  guides(color=guide_legend(nrow=1)) + 
  theme(legend.position="bottom") +
  scale_color_discrete(name="Design:")  +
  scale_shape_discrete(name="Design:")  +
    scale_y_continuous(breaks=c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8), limits=c(0, 0.75))
g_ratio
```


# Design 2

## All Settings

### Absolute MSE


```{r mse-design2-dfJ, fig.height=4.5, fig.width=4.5}
g_ratio <- MSE_results %>%
  filter(design %in% c(2)) %>%
  filter(!setting %in% c("B2")) %>%
  rename(Trend=setting) %>%
  mutate(Design=case_when(design==1~"1 -- Parallel",
                          design==2~"2 -- Parallel, Staggered Baseline")) %>%
  filter(model %in% c("splinetime2", "wgroup", "hh_avg")) %>%
  ggplot() +
  theme_bw() +
  geom_path(aes(x=J,
                 y=value,
                 col=as.factor(Model))) +
  geom_point(aes(x=J,
                 y=value,
                 col=as.factor(Model),
                 shape=as.factor(Model))) +
  ylab("MSE") + 
  xlab("Number of Measurements per Household (J)")+ 
  facet_wrap(~Trend,
             scales="free_x",
             labeller=labeller(Trend = label_both,
                               design= label_both)) +
  guides(color=guide_legend(nrow=1)) + 
  theme(legend.position="bottom") +
  scale_color_discrete(name="Design:")  +
  scale_shape_discrete(name="Design:")  +
    scale_y_continuous(breaks=c(0, 0.1, 0.2, 0.3, 0.4, 0.5), limits=c(0, 0.55))
g_ratio
```


### Absolute RMSE

```{r rmse-design2-dfJ, fig.height=4.5, fig.width=4.5}
g_ratio <- MSE_results %>%
  filter(design %in% c(2)) %>%
  filter(!setting %in% c("B2")) %>%
  rename(Trend=setting) %>%
  mutate(Design=case_when(design==1~"1 -- Parallel",
                          design==2~"2 -- Parallel, Staggered Baseline")) %>%
  filter(model %in% c("splinetime2", "wgroup", "hh_avg")) %>%
  ggplot() +
  theme_bw() +
  geom_path(aes(x=J,
                 y=sqrt(value),
                 col=as.factor(Model))) +
  geom_point(aes(x=J,
                 y=sqrt(value),
                 col=as.factor(Model),
                 shape=as.factor(Model))) +
  ylab(expression("RMSE (Log "~mu~"g/m"^3~")")) +
  xlab("Number of Measurements per Household (J)")+ 
  facet_wrap(~Trend,
             scales="free_x",
             labeller=labeller(Trend = label_both,
                               design= label_both)) +
  guides(color=guide_legend(nrow=1)) + 
  theme(legend.position="bottom") +
  scale_color_discrete(name="Design:")  +
  scale_shape_discrete(name="Design:")  +
    scale_y_continuous(breaks=c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8), limits=c(0, 0.75))
g_ratio
```

# Designs 1 and 2


## Relative MSE 

This compares the relative MSE for  model without time to model with time. Using splinetime2 as the reference category.

```{r relmse-designs12-dfJ, fig.height=4.5, fig.width=4.5}
# Plot MSE ratio, ignoring time to including time
# Comparison is splinetime2
g_ratio <- sim_results %>%
  filter(design %in% c(1, 2)) %>%
  rename(Trend=setting) %>%
  mutate(Design=case_when(design==1~"1 -- Parallel",
                          design==2~"2 -- Parallel, Staggered Baseline")) %>%
  ggplot() +
  theme_bw() +
  geom_hline(aes(yintercept=1)) +
  # geom_point(aes(x=J,
  #                y=MSE_ratio_hh,
  #                col="1")) +
  geom_path(aes(x=J,
                 y=RMSE_ratio2_notime,
                 col=Design)) +
  geom_point(aes(x=J,
                 y=RMSE_ratio2_notime,
                 col=Design,
                 shape=Design)) +
  ylab("Relative RMSE") + 
  xlab("Number of Measurements per Household (J)")+ 
  facet_wrap(~Trend,
             scales="free_x",
             labeller=labeller(Trend = label_both,
                               design= label_both)) +
  guides(color=guide_legend(nrow=1)) + 
  theme(legend.position="bottom") +
  scale_color_discrete(name="Design:")  +
  scale_shape_discrete(name="Design:") 
g_ratio
```



# Other Designs (3-7)

## RMSE

```{r rmse-designs6911, fig.width=6.5, fig.height=8}
# Plot MSE ratio, ignoring time to including time
g_ratio <- MSE_results %>%
  filter(setting!="B2") %>%
  filter(design %in% c(3:7)) %>%
    rename(Trend=setting) %>%
  mutate(Design=case_when(design==3~"3 -- Parallel, Aligned Baseline, 4 Obs.",
                          design==4~"4 -- Parallel, Staggered Baseline, 4 Obs.",
                          design==5~"5 -- Parallel, Staggered Baseline, 6 Obs.",
                          design==6~"6 -- Stepped Wedge, Aligned Baseline, 6 Obs.",
                          design==7~"7 -- Stepped Wedge, Staggered Baseline, 6 Obs.")) %>%
      filter(!model %in% c("factime")) %>%

  ggplot() +
  theme_bw() +
  geom_point(aes(x=Trend,
                 shape=Model,
                 col=Model,
                 y=sqrt(value)),
                 position=position_jitter(height=0, width=0.1)) +
  ylab(expression("RMSE (Log "~mu~"g/m"^3~")")) +
  facet_wrap(~Design, ncol=2) +
  guides(color=guide_legend(nrow=2)) + 
  theme(legend.position="bottom") +
  scale_color_discrete(name="Model:")  +
  scale_shape_discrete(name="Model:")
g_ratio
```


```{r rmse-designs6911-n50, fig.width=6.5, fig.height=8}
# Plot MSE ratio, ignoring time to including time
g_ratio <- MSE_results_n50 %>%
  filter(setting!="B2") %>%
  filter(design %in% c(3:7)) %>%
    rename(Trend=setting) %>%
    
  mutate(Design=case_when(design==3~"3 -- Parallel, Aligned Baseline, 4 Obs.",
                          design==4~"4 -- Parallel, Staggered Baseline, 4 Obs.",
                          design==5~"5 -- Parallel, Staggered Baseline, 6 Obs.",
                          design==6~"6 -- Stepped Wedge, Aligned Baseline, 6 Obs.",
                          design==7~"7 -- Stepped Wedge, Staggered Baseline, 6 Obs.")) %>%
      filter(!model %in% c("factime")) %>%

  ggplot() +
  theme_bw() +
  geom_point(aes(x=Trend,
                 shape=Model,
                 col=Model,
                 y=sqrt(value)),
                 position=position_jitter(height=0, width=0.1)) +
  ylab(expression("RMSE (Log "~mu~"g/m"^3~")")) +
  facet_wrap(~Design, ncol=2) +
  guides(color=guide_legend(nrow=2)) + 
  theme(legend.position="bottom") +
  scale_color_discrete(name="Model:")  +
  scale_shape_discrete(name="Model:")
g_ratio
```


## Relative RMSE version


```{r relrmse-designs6911-df2, fig.width=4.5, fig.height=4.5}
# Plot MSE ratio, ignoring time to including time
g_ratio <- sim_results %>%
  filter(setting!="B2") %>%
  filter(design %in% c(3:7)) %>%

    rename(Trend=setting) %>%
  mutate(Design=case_when(design==3~"3 -- Parallel, Aligned Baseline, 4 Obs.",
                          design==4~"4 -- Parallel, Staggered Baseline, 4 Obs.",
                          design==5~"5 -- Parallel, Staggered Baseline, 6 Obs.",
                          design==6~"6 -- Stepped Wedge, Aligned Baseline, 6 Obs.",
                          design==7~"7 -- Stepped Wedge, Staggered Baseline, 6 Obs.")) %>%
  ggplot() +
  theme_bw() +
  geom_hline(aes(yintercept=1)) +
  geom_point(aes(x=Trend,
                 shape=Design,
                 col=Design,
                 y=RMSE_ratio2_notime),
             position=position_jitter(height=0, width=0.1)) +
  ylab("Relative RMSE") + 
  guides(color=guide_legend(nrow=5)) + 
  theme(legend.position="bottom") +
  scale_color_discrete(name="Design:")  +
  scale_shape_discrete(name="Design:")

g_ratio
```


